\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-02 paper.tex
last version at 2:10:14:15:00

On the other hand, educational robots can be of great use in making young school
kids interested in technological developments~\cite{cooper1999robots,
wyffels2010building}. It is important to know about the key socio-cognitive
features of this subset of human-robot interaction because these features let
the researchers design better interactive scenarios in the future. These
features include the conceptual mapping of the sensor data visualisation and the
robot's function and the generalising the concepts to solve a given problem in a
contextual learning environment.

Thymio II~\cite{riedo2012two} can provide salient effects onto our visual
attention through the LEDs. We can use this feature to guide the users'
attention in a way that the effectiveness of the interaction is maximised. In
the case of interaction with the educational robots the effect of the
interaction is to make the users understand the technical aspects of the robot
and to make the users be able to transfer it to different domains.

@@

>>>>

%On the other hand, educational robots can be of great use in making young school
%kids interested in technological developments~\cite{cooper1999robots,
%wyffels2010building}. It is important to know about the key socio-cognitive
%features of this subset of human-robot interaction because these features let
%the researchers design better interactive scenarios in the future. These
%features include the conceptual mapping of the sensor data visualisation and the
%robot's function and the generalising the concepts to solve a given problem in a
%contextual learning environment.
%
%Thymio II~\cite{riedo2012two} can provide salient effects onto our visual
%attention through the LEDs. We can use this feature to guide the users'
%attention in a way that the effectiveness of the interaction is maximised. In
%the case of interaction with the educational robots the effect of the
%interaction is to make the users understand the technical aspects of the robot
%and to make the users be able to transfer it to different domains.

@@

\paragraph{Article overview}
\fixme{write it}
